3D Magnetic modelling of ellipsoidal bodies

### 2017-01-18 manuscript/manuscript.tex
demagnetizing field within ellipsoids

\citep{dubois1896}: The magnetisation induced in a uniform field is not necessarily 
also uniform.
A vector is said to be distributed uniformly when at
every point throughout the region considered it has the same
direction and the same value.
It maybe mathematically proved that such
uniformity only holds for bodies of an ellipsoidal shape.
If one axis coincides with the direction of the field, 
the magnetisation is in the same direction as that axis.
The demagnetising intensity for unit magnetisation we 
shall again speak of as the demagnetising
factor for the axial direction in question.

@@

\subsection{Geometrical parameters defining ellipsoids}

@@

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre.
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in equation \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
is defined according to equations \ref{eq:V_triaxial_prolate} or
\ref{eq:V_oblate}, depending on the ellipsoid type.

@@

\subsection{Magnetic scalar potential }

The methods commonly applied in the magnetic modelling of
ellipsoidal bodies make use of an auxiliary variable $\lambda$,
which is a real number.

>>>>

@@

\subsection{Geometrical parameters and coordinate systems}

@@

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre.
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in equation \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
is defined according to equations \ref{eq:V_triaxial_prolate} or
\ref{eq:V_oblate}, depending on the ellipsoid type.
Afterwards, we use the superscript "$\sim$" to implicitly
define quantities referred to a local coordinate system.

@@

\subsection{Demagnetizing field within ellipsoids}

Consider a magnetized ellipsoid immersed in
a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$).
The total magnetic intensity field $\mathbf{H}(\mathbf{r})$
at the position $\mathbf{r}$ (equations \ref{eq:A} and \ref{eq:coord_transformation}) 
of a point referred to the main coordinate system is defined
as follows
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla \phi(\mathbf{r}) \: ,
\label{eq:total-H-field}
\end{equation}
where the second term, representing the induced magnetic field,
is the negative gradient of the magnetic scalar potential 
$\phi(\mathbf{r})$ given by
\begin{equation}
\phi(\mathbf{r}) = \frac{1}{4\pi} \iiint_{V} 
\mathbf{J}(\mathbf{r}^{\prime})^{\top} \left(
\frac{\mathbf{r} - \mathbf{r}^{\prime}}{\| \mathbf{r} - \mathbf{r}^{\prime} \|^{3}}
\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:phi-potential}
\end{equation}
In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
is the position vector of a point located within the volume $V$, 
the integral is conducted over the variables 
$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ representing
the coordinates of a point located within the volume $V$
of the ellipsoid, $\| \cdot \|$ denotes the Euclidean norm and 
$\mathbf{J}(\mathbf{r}^{\prime})$ is the magnetization vector
(in $\unit{Am^{-1}}$).
Equation \ref{eq:total-H-field} is valid anywhere, 
independently if the position vector $\mathbf{r}$ represents
a point located inside or outside the magnetized body.

According to \citet{maxwell1873}, the only finite bodies that 
can be uniformly magnetized in the presence of a uniform and static 
magnetic field are the ones bounded by surfaces of second degree, which
are ellipsoids.

This property comes from the fact that the gravitational potential
within an ellipsoid with uniform density is a quadratic function
of the spatial coordinates.

Based on this, the magnetization vector 
$\mathbf{J}(\mathbf{r}^{\prime})$ (equation \ref{eq:phi-potential})
can be moved outside the integral, resulting that
%\begin{equation}
%
%\label{eq:total-H-field-matrix}
%\end{equation}
